### 2017-03-13 thesis/misc/appendix.tex
Divided the appendix file into two - tmp commit
Need to add linear model prediction scatter plots - tmp commit

	\section{Metagenes created from raw data and standardised data in Creighton \textit{et al.} data set}
	\label{sec:metagenes_created_from_raw_data_vs_standardised_data}

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/check_raw_vs_std_mg}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/check_raw_vs_std_mg}
		\caption{Scatter plots showing the raw and ranked obesity metagene scores generated from raw or standardised Creighton \textit{et al.} data set. }
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

	\section{Metagenes created from raw data and standardised data (ICGC)}
	\label{sec:metagenes_created_from_raw_data_vs_standardised_data_icgc}

	% \begin{figure}[h]
	% 	\centering
	% 	\includegraphics[width=0.45\linewidth,page=1]{appendix/crtcga_raw_vs_std}
	% 	\hfill
	% 	\includegraphics[width=0.45\linewidth,page=2]{appendix/crtcga_raw_vs_std}
	% 	\caption{appendix/Check_raw_vs_std}
	% 	\label{fig:appendix/check_raw_vs_std}
	% \end{figure}

	\section{Rest of the ICGC cancer heatmap resutls}
	\label{sec:rest_of_the_icgc_cancer_heatmap_resutls}

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/crtcga_std}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/crtcga_std}
		\caption{appendix/Check_raw_vs_std}
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

	\section{FM metagene, raw vs std}
	\label{sec:fm_metagene_raw_vs_std}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=1,width=0.8\linewidth]{appendix/fm_meta_check}
		\caption{appendix/fm_meta_check}
		\label{fig:appendix/fm_meta_check}
	\end{figure}

	\section{Creighton DEG metagene direction}
	\label{sec:creighton_deg_metagene_direction}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=1,width=0.8\linewidth]{cr_meta_direction}
		\caption{cr_meta_direction}
		\label{fig:cr_meta_direction}
	\end{figure}

	\section{Number of gene probes/genes in each signature}
	\label{app:number_of_gene_probes_genes_in_each_signature}

	\begin{table}[htbp]
		\centering
		\caption{Summary of the number of gene probes and genes in each obesity associated genetic signature}
		\label{tab:signature_gene_num}
		\begin{tabular}{lcc}
			Obesity associated genetic signature & No. gene probes   & No. genes\\
			\hline
			\rule{0pt}{2.25ex}Original & 799 & 644\\
			Cr                         & 799 & 678\\
			Res                        & 799 & 655\\
			Ca                         & 799 & 657\\
			CaRes                      & 799 & 651\\
			CrOl                       & 239 & 199\\
			ResOl                      & 168 & 147\\
			CaOl                       & 148 & 128\\
			CaResOl                    & 92  & 86\\
			\hline
			\hline
		\end{tabular}
	\end{table}

	\chapter{Additional results from \cref{cha:obesity_associated_genetic_signature_and_pathway_signatures}}
	\label{app:b}

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.7\linewidth]{results2/gatzares1}
		\caption{results from gatza's study}
		\label{fig:gatza_paper_res}
	\end{figure}

% [1] "crolgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.553214  0.123891 4.465  2.16e-05 ***
% bmi                 -0.001629 0.004071 -0.400 0.69
% (Intercept)         0.55700   0.05464  10.194 <2e-16   ***
% bmiStatusobese      -0.10551  0.07021  -1.503 0.136
% bmiStatusoverweight -0.02165  0.07727  -0.280 0.780
% (Intercept)         0.307513  0.163530 1.880  0.0631   .
% bmi                 0.011279  0.006976 1.617  0.1092
% bmiStatusobese      -0.261145 0.118795 -2.198 0.0304   *
% bmiStatusoverweight -0.079845 0.084661 -0.943 0.3480
% (Intercept)         0.007141  0.382725 0.019  0.9852
% bcat_probes         0.156062  0.223779 0.697  0.4873
% er_probes           0.123403  0.254800 0.484  0.6293
% ifna_probes         -0.430229 0.497301 -0.865 0.3892
% ifng_probes         0.378437  0.509352 0.743  0.4594
% myc_probes          0.160785  0.229142 0.702  0.4846
% pr_probes           0.597403  0.244252 2.446  0.0164   *
% (Intercept)         0.055088  0.389472 0.141  0.8878
% bmi                 -0.002745 0.003814 -0.720 0.4736
% bcat_probes         0.179900  0.226799 0.793  0.4297
% er_probes           0.125413  0.255485 0.491  0.6247
% ifna_probes         -0.475417 0.502546 -0.946 0.3466
% ifng_probes         0.429131  0.515526 0.832  0.4074
% myc_probes          0.184642  0.232124 0.795  0.4284
% pr_probes           0.607982  0.245336 2.478  0.0151   *
% (Intercept)         0.01666   0.37989  0.044  0.9651
% bmiStatusobese      -0.11197  0.06602  -1.696 0.0933   .
% bmiStatusoverweight -0.02348  0.07151  -0.328 0.7434
% bcat_probes         0.22035   0.22616  0.974  0.3325
% er_probes           0.10450   0.25330  0.413  0.6809
% ifna_probes         -0.60343  0.50372  -1.198 0.2341
% ifng_probes         0.54671   0.51484  1.062  0.2911
% myc_probes          0.21341   0.22998  0.928  0.3559
% pr_probes           0.59491   0.24257  2.453  0.0161   *
% (Intercept)         -0.128149 0.393204 -0.326 0.7453
% bmi                 0.008834  0.006565 1.346  0.1819
% bmiStatusobese      -0.234634 0.112386 -2.088 0.0397   *
% bmiStatusoverweight -0.067942 0.078484 -0.866 0.3890
% bcat_probes         0.216892  0.225167 0.963  0.3380
% er_probes           0.081506  0.252745 0.322  0.7478
% ifna_probes         -0.625864 0.501740 -1.247 0.2155
% ifng_probes         0.546873  0.512538 1.067  0.2889
% myc_probes          0.196215  0.229305 0.856  0.3945
% pr_probes           0.560706  0.242816 2.309  0.0232   *

% [1] "resobsgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.547104  0.123915 4.415  2.62e-05 ***
% bmi                 -0.001422 0.004072 -0.349 0.728
% (Intercept)         0.547619  0.054641 10.022 <2e-16   ***
% bmiStatusobese      -0.096832 0.070212 -1.379 0.171
% bmiStatusoverweight -0.001804 0.077273 -0.023 0.981
% (Intercept)         0.298589  0.163546 1.826  0.0710   .
% bmi                 0.011259  0.006976 1.614  0.1099
% bmiStatusobese      -0.252186 0.118807 -2.123 0.0364   *
% bmiStatusoverweight -0.059898 0.084669 -0.707 0.4810
% (Intercept)         0.18694   0.36963  0.506  0.6142
% bcat_probes         0.09717   0.21612  0.450  0.6541
% er_probes           0.07879   0.24608  0.320  0.7496
% ifna_probes         -0.17576  0.48029  -0.366 0.7152
% ifng_probes         0.07930   0.49193  0.161  0.8723
% myc_probes          -0.04517  0.22130  -0.204 0.8387
% pr_probes           0.59554   0.23590  2.525  0.0133   *
% (Intercept)         0.221757  0.376612 0.589  0.5574
% bmi                 -0.001994 0.003688 -0.540 0.5902
% bcat_probes         0.114479  0.219311 0.522  0.6029
% er_probes           0.080247  0.247050 0.325  0.7461
% ifna_probes         -0.208580 0.485954 -0.429 0.6688
% ifng_probes         0.116119  0.498505 0.233  0.8163
% myc_probes          -0.027845 0.224460 -0.124 0.9015
% pr_probes           0.603222  0.237235 2.543  0.0127   *
% (Intercept)         0.195965  0.367384 0.533  0.5951
% bmiStatusobese      -0.096834 0.063844 -1.517 0.1328
% bmiStatusoverweight -0.004412 0.069155 -0.064 0.9493
% bcat_probes         0.150379  0.218719 0.688  0.4935
% er_probes           0.058880  0.244961 0.240  0.8106
% ifna_probes         -0.344126 0.487134 -0.706 0.4817
% ifng_probes         0.242697  0.497893 0.487  0.6271
% myc_probes          -0.001285 0.222407 -0.006 0.9954
% pr_probes           0.591191  0.234582 2.520  0.0135   *
% (Intercept)         0.041459  0.379420 0.109  0.9132
% bmi                 0.009426  0.006335 1.488  0.1403
% bmiStatusobese      -0.227717 0.108446 -2.100 0.0386   *
% bmiStatusoverweight -0.051853 0.075733 -0.685 0.4953
% bcat_probes         0.146687  0.217273 0.675  0.5013
% er_probes           0.034350  0.243884 0.141  0.8883
% ifna_probes         -0.368065 0.484150 -0.760 0.4491
% ifng_probes         0.242870  0.494570 0.491  0.6246
% myc_probes          -0.019634 0.221267 -0.089 0.9295
% pr_probes           0.554701  0.234304 2.367  0.0201   *

% [1] "rescrolgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%               Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.5343899  0.1239554 4.311  3.9e-05 ***
% bmi                 -0.0009922 0.0040730 -0.244 0.808
% (Intercept)         0.54870    0.05482   10.009 <2e-16  ***
% bmiStatusobese      -0.09063   0.07044   -1.287 0.201
% bmiStatusoverweight -0.01515   0.07753   -0.195 0.845
% (Intercept)         0.304200   0.164179  1.853  0.0670  .
% bmi                 0.011054   0.007003  1.578  0.1178
% bmiStatusobese      -0.243160  0.119267  -2.039 0.0442  *
% bmiStatusoverweight -0.072189  0.084997  -0.849 0.3978
% (Intercept)         0.17069    0.37929   0.450  0.6537
% bcat_probes         0.09532    0.22177   0.430  0.6683
% er_probes           0.03171    0.25251   0.126  0.9004
% ifna_probes         -0.57965   0.49283   -1.176 0.2426
% ifng_probes         0.50919    0.50478   1.009  0.3157
% myc_probes          0.06345    0.22708   0.279  0.7805
% pr_probes           0.54200    0.24206   2.239  0.0276  *
% (Intercept)         0.204758   0.386507  0.530  0.5976
% bmi                 -0.001950  0.003785  -0.515 0.6076
% bcat_probes         0.112257   0.225072  0.499  0.6192
% er_probes           0.033134   0.253540  0.131  0.8963
% ifna_probes         -0.611750  0.498720  -1.227 0.2231
% ifng_probes         0.545210   0.511601  1.066  0.2894
% myc_probes          0.080405   0.230357  0.349  0.7279
% pr_probes           0.549516   0.243468  2.257  0.0264  *
% (Intercept)         0.17933    0.37777   0.475  0.636
% bmiStatusobese      -0.09681   0.06565   -1.475 0.144
% bmiStatusoverweight -0.01219   0.07111   -0.171 0.864
% bcat_probes         0.14969    0.22490   0.666  0.507
% er_probes           0.01354    0.25189   0.054  0.957
% ifna_probes         -0.73888   0.50091   -1.475 0.144
% ifng_probes         0.66381    0.51197   1.297  0.198
% myc_probes          0.10813    0.22869   0.473  0.638
% pr_probes           0.53872    0.24121   2.233  0.028   *
% (Intercept)         0.027729   0.390580  0.071  0.9436
% bmi                 0.009248   0.006522  1.418  0.1596
% bmiStatusobese      -0.225233  0.111636  -2.018 0.0466  *
% bmiStatusoverweight -0.058734  0.077961  -0.753 0.4532
% bcat_probes         0.146066   0.223664  0.653  0.5154
% er_probes           -0.010526  0.251058  -0.042 0.9667
% ifna_probes         -0.762373  0.498391  -1.530 0.1296
% ifng_probes         0.663981   0.509117  1.304  0.1955
% myc_probes          0.090122   0.227775  0.396  0.6933
% pr_probes           0.502919   0.241196  2.085  0.0399  *

% [1] "caobsgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

% Coefficients:
%              Estimate Std. Error t value Pr(>|t|)
% (Intercept)         0.538968  0.123943 4.349  3.39e-05 ***
% bmi                 -0.001147 0.004073 -0.282 0.779
% (Intercept)         0.53896   0.05458  9.875  2.76e-16 ***
% bmiStatusobese      -0.08982  0.07013  -1.281 0.203
% bmiStatusoverweight 0.01804   0.07719  0.234  0.816
% (Intercept)         0.27986   0.16317  1.715  0.0896   .
% bmi                 0.01171   0.00696  1.683  0.0957   .
% bmiStatusobese      -0.25146  0.11853  -2.121 0.0365   *
% bmiStatusoverweight -0.04241  0.08447  -0.502 0.6168
% (Intercept)         0.12454   0.38803  0.321  0.7490
% bcat_probes         0.14068   0.22688  0.620  0.5367
% er_probes           0.11597   0.25833  0.449  0.6545
% ifna_probes         -0.33319  0.50420  -0.661 0.5104
% ifng_probes         0.30871   0.51641  0.598  0.5515
% myc_probes          -0.04569  0.23232  -0.197 0.8445
% pr_probes           0.56692   0.24764  2.289  0.0243   *
% (Intercept)         0.162063  0.395326 0.410  0.6828
% bmi                 -0.002148 0.003872 -0.555 0.5804
% bcat_probes         0.159335  0.230208 0.692  0.4906
% er_probes           0.117547  0.259326 0.453  0.6514
% ifna_probes         -0.368552 0.510101 -0.723 0.4718
% ifng_probes         0.348376  0.523276 0.666  0.5072
% myc_probes          -0.027017 0.235613 -0.115 0.9090
% pr_probes           0.575201  0.249024 2.310  0.0232   *
% (Intercept)         0.134514  0.384960 0.349  0.7276
% bmiStatusobese      -0.099695 0.066899 -1.490 0.1397
% bmiStatusoverweight 0.008987  0.072463 0.124  0.9016
% bcat_probes         0.193430  0.229183 0.844  0.4009
% er_probes           0.092451  0.256681 0.360  0.7196
% ifna_probes         -0.522336 0.510440 -1.023 0.3089
% ifng_probes         0.492130  0.521713 0.943  0.3481
% myc_probes          -0.001892 0.233048 -0.008 0.9935
% pr_probes           0.560583  0.245805 2.281  0.0249   *
% (Intercept)         -0.028482 0.397505 -0.072 0.9430
% bmi                 0.009944  0.006637 1.498  0.1376
% bmiStatusobese      -0.237770 0.113616 -2.093 0.0392   *
% bmiStatusoverweight -0.041061 0.079343 -0.518 0.6061
% bcat_probes         0.189535  0.227630 0.833  0.4073
% er_probes           0.066573  0.255509 0.261  0.7950
% ifna_probes         -0.547591 0.507227 -1.080 0.2832
% ifng_probes         0.492312  0.518143 0.950  0.3446
% myc_probes          -0.021250 0.231813 -0.092 0.9272
% pr_probes           0.522087  0.245472 2.127  0.0362   *

% [1] "cacrolgene"

% Call:
% lm(formula = as.formula(formula_txt[j]), data = data)

>>>>

	\section{Comparison of the Creighton \textit{et al.} obesity metagene in standardised or non-standardised CR data}
	\label{sec:metagenes_created_from_raw_data_vs_standardised_data}

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/check_raw_vs_std_mg}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/check_raw_vs_std_mg}
		\caption{Scatter plots showing the raw and ranked Creighton \textit{et al.} obesity metagene values generated from standardised or non-standardised CR data set. }
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

	\section{Comparison of the Creighton \textit{et al.} obesity metagene in standardised or non-standardised \gls{icgc} data}
	\label{sec:comp_cr_raw_std_icgc}

	As shown in \cref{fig:appendix/check_raw_vs_std}, the Creighton \textit{et al.} obesity metagene values generated from the transformation matrices (from standardised or non-standardised CR data) were more consistent (or less variable) in the standardised \gls{icgc} \gls{blca} data, compared with the non-standardised data.
	Results from \cref{fig:appendix/check_raw_vs_std_tm} suggested that there was no obvious difference in the quality of the metagenes generated from standardised or non-standardised TM.
	Only the results from \gls{blca} data set are shown, as the results from the other \gls{icgc} cancer types showed very similar results.

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\linewidth,page=1]{appendix/crtcga_raw_vs_std}
		\hfill
		\includegraphics[width=0.45\linewidth,page=2]{appendix/crtcga_raw_vs_std}\\
		\caption{Scatter plots comparing the Creighton \textit{et al.} obesity metagene generated from transformation matrix (from standardised or non-standardised CR data) in non-standardised (left) and standardised (right) \gls{icgc} \gls{blca} data.}
		\label{fig:appendix/check_raw_vs_std}
	\end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\linewidth,page=3]{appendix/crtcga_raw_vs_std}
		\hfill
		\includegraphics[width=0.45\linewidth,page=4]{appendix/crtcga_raw_vs_std}\\
		\caption{Scatter plots comparing the Creighton \textit{et al.} obesity metagene generated from transformation matrix from non-standardisedright (left) or standardised (right) CR data in non-standardised  and standardised  \gls{icgc} \gls{blca} data.}
		\label{fig:appendix/check_raw_vs_std_tm}
	\end{figure}

	\section{Remainder of the results of Creighton \textit{et al.} obesity metagenes in the \gls{icgc} cancer data sets}
	\label{sec:rest_of_the_cr_icgc_cancer_heatmap_results}

	As shown in \cref{fig:appendix/cr_icgc_heatmap}, the original obesity metagene from the Creighton \textit{et al.} study was reflective of the sample gene expression levels of the obesity associated genetic signature in all of the other \gls{icgc} cancer data sets.
	However, none of the \gls{icgc} cancer data sets (other than the \gls{blca} data set; \cref{fig:crmetaicgc} in \cref{sec:creighton_obesity_metagene}) showed any significant association of the sample \gls{bmi} or \gls{bmi} status with the Or obesity metagene (\cref{fig:appendix/cr_icgc_box_scatter}).
	The heatmaps, box plots and scatter plots for the other CR obesity metagenes in other \gls{icgc} cancer types are not shown, as many of the plots were very similar to the plots from the \gls{blca} data set.
	The statistics from the results of the box and scatter plots in the other \gls{icgc} cancer types were summarised in \cref{tab:degmetacesc,tab:degmetacoad,tab:degmetakirp,tab:degmetalihc,tab:degmetaread,tab:degmetaskcm,tab:degmetaucec}.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=13]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=28]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/crtcga_std}\\
		\caption{Heatmaps showing the association of obesity metagene from the \citet{Creighton2012} study with sample gene expression from the other \gls{icgc} data sets.
	Level of expression is represented in the top right histogram, where low and high gene expression were colour-coded with blue and red, respectively.
	Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from the \gls{icgc} data.
	The obesity associated metagene scores of the samples are shown in a separate row at top of the heatmap, and the tree diagram of the heirarchical clustering of the genes is shown to the left of the heatmap. }
		\label{fig:appendix/cr_icgc_heatmap}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=9,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=10,width=0.45\linewidth]{appendix/crtcga_std}\\
		\includegraphics[page=14,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/crtcga_std}\\
		\caption{Box plots and scatter plots showing the association of obesity metagene from the \citet{Creighton2012} study with the sample \gls{bmi} status  and \gls{bmi} from the other \gls{icgc} data sets, respectively.
	In the box plot, the p-values above the groups represent the statistical significance of the association of the metagene with the overweight or obese group compared with the normal weight group.
	The \gls{anova} p-value shows the statistical significance of the association of the metagene with the sample \gls{bmi} groups.
	In the scatter plot, $R^2$- and p-values describe the adjusted coefficient of determination of the regression line and the statistical significance of the linear model used to draw the regression line, respectively.}
		\label{fig:appendix/cr_icgc_box_scatter}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=19,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/crtcga_std}\\
		\includegraphics[page=24,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/crtcga_std}\\
		\includegraphics[page=29,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/crtcga_std}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=34,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/crtcga_std}\\
		\includegraphics[page=39,width=0.45\linewidth]{appendix/crtcga_std}
		\hfill
		\includegraphics[page=40,width=0.45\linewidth]{appendix/crtcga_std}\\
		\caption{Name}
	\end{figure}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{cesc} cancer data}
	\label{tab:degmetacesc}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.9332                      & 0.5302  & 0.7622             & -0.003950  & 0.7265              \\
            Res     & 0.9205                      & 0.3369  & 0.6043             & 0.004249   & 0.8122              \\
            CrOl    & 0.8940                      & 0.1430  & 0.2959             & -0.0004927 & 0.3465              \\
            ResOl   & 0.9930                      & 0.1705  & 0.3078             & 0.003263   & 0.1898              \\
            Ca      & 0.8861                      & 0.3616  & 0.6426             & -0.003307  & 0.6073              \\
            CaRes   & 0.8323                      & 0.3330  & 0.6167             & -0.003832  & 0.7001              \\
            CaOl    & 0.9124                      & 0.1602  & 0.2600             & -0.001612  & 0.4242              \\
            CaResOl & 0.9646                      & 0.1663  & 0.2863             & 0.003097   & 0.1946              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{coad} cancer data}
	\label{tab:degmetacoad}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.2843                      & 0.8176  & 0.5460             & -0.004373  & 0.8865              \\
            Res     & 0.4091                      & 0.8473  & 0.7064             & -0.004243  & 0.8245              \\
            CrOl    & 0.4063                      & 0.9295  & 0.6150             & -0.00397   & 0.7400              \\
            ResOl   & 0.3748                      & 0.8484  & 0.5295             & -0.004020  & 0.7532              \\
            Ca      & 0.6507                      & 0.7692  & 0.7579             & -0.002493  & 0.5075              \\
            CaRes   & 0.4565                      & 0.9808  & 0.7161             & -0.004278  & 0.8385              \\
            CaOl    & 0.2931                      & 0.9217  & 0.4621             & -0.00425   & 0.8273              \\
            CaResOl & 0.4203                      & 0.9087  & 0.7017             & -0.004461  & 0.9800              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{kirp} cancer data}
	\label{tab:degmetakirp}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.1853                      & 0.2590  & 0.3387             & -0.005657  & 0.5798              \\
            Res     & 0.1063                      & 0.1825  & 0.2128             & -0.005037  & 0.5368              \\
            CrOl    & 0.2576                      & 0.1757  & 0.3162             & -0.005763  & 0.5879              \\
            ResOl   & 0.3120                      & 0.1738  & 0.3198             & -0.004513  & 0.5048              \\
            Ca      & 0.2431                      & 0.2142  & 0.3591             & -0.005582  & 0.5743              \\
            CaRes   & 0.2327                      & 0.2344  & 0.3738             & -0.006250  & 0.6279              \\
            CaOl    & 0.3426                      & 0.2775  & 0.4693             & -0.007333  & 0.77469             \\
            CaResOl & 0.2643                      & 0.1315  & 0.2410             & -0.001408  & 0.3649              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{lihc} cancer data}
	\label{tab:degmetalihc}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.4033                      & 0.2900  & 0.5221             & 0.006348   & 0.1028              \\
            Res     & 0.5008                      & 0.8743  & 0.8004             & -0.0003709 & 0.3430              \\
            CrOl    & 0.7599                      & 0.8562  & 0.9189             & -0.001554  & 0.4424              \\
            ResOl   & 0.9238                      & 0.9773  & 0.9938             & -0.001283  & 0.4162              \\
            Ca      & 0.4898                      & 0.8221  & 0.7917             & 0.0005899  & 0.2834              \\
            CaRes   & 0.5976                      & 0.9929  & 0.8638             & -0.001090  & 0.3990              \\
            CaOl    & 0.8717                      & 0.8834  & 0.9679             & -0.002010  & 0.4925              \\
            CaResOl & 0.5369                      & 0.7185  & 0.7073             & -0.0004212 & 0.3465              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{read} cancer data}
	\label{tab:degmetaread}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.9129                      & 0.4008  & 0.5942             & -0.0132    & 0.8038              \\
            Res     & 0.7737                      & 0.2244  & 0.4308             & -0.008917  & 0.5484              \\
            CrOl    & 0.8439                      & 0.1283  & 0.2643             & 0.001024   & 0.3036              \\
            ResOl   & 0.6953                      & 0.06841 & 0.1766             & 0.01099    & 0.1840              \\
            Ca      & 0.6298                      & 0.1326  & 0.2960             & -0.001242  & 0.3432              \\
            CaRes   & 0.6302                      & 0.1053  & 0.2453             & 0.001989   & 0.2885              \\
            CaOl    & 0.6871                      & 0.1411  & 0.3358             & -0.004847  & 0.4219              \\
            CaResOl & 0.8821                      & 0.08474 & 0.1817             & 0.001095   & 0.3025              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{skcm} cancer data}
	\label{tab:degmetaskcm}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.7115                      & 0.3329  & 0.6264             & 0.002887   & 0.2033              \\
            Res     & 0.7604                      & 0.5408  & 0.6396             & -0.001725  & 0.4296              \\
            CrOl    & 0.4719                      & 0.1224  & 0.2913             & 0.01261    & 0.05347             \\
            ResOl   & 0.8640                      & 0.1668  & 0.3051             & 0.01541    & {\bfseries 0.0372}\tnote{1}  \\
            Ca      & 0.8792                      & 0.2084  & 0.3739             & 0.006674   & 0.1184              \\
            CaRes   & 0.8098                      & 0.1950  & 0.3677             & 0.005746   & 0.1347              \\
            CaOl    & 0.9478                      & 0.2726  & 0.4471             & 0.01009    & 0.07449             \\
            CaResOl & 0.7309                      & 0.2561  & 0.2830             & 0.01606    & {\bfseries 0.03421} \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Statistics of all the obesity metagenes in \gls{ucec} cancer data}
	\label{tab:degmetaucec}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.8357                      & 0.08117 & 0.1039             & 0.006952   & {\bfseries 0.03716}\tnote{1}\\
            Res     & 0.8664                      & 0.2023  & 0.3131             & 0.001998   & 0.1619              \\
            CrOl    & 0.9251                      & 0.3800  & 0.5800             & -0.000311  & 0.3569              \\
            ResOl   & 0.5826                      & 0.09608 & 0.2156             & 0.003487   & 0.1021              \\
            Ca      & 0.7491                      & 0.1103  & 0.1905             & 0.003811   & 0.09260             \\
            CaRes   & 0.8086                      & 0.2002  & 0.3419             & 0.0005824  & 0.2584              \\
            CaOl    & 0.9068                      & 0.2672  & 0.4153             & 0.00305    & 0.1166              \\
            CaResOl & 0.8360                      & 0.2440  & 0.4034             & 0.00022898 & 0.2863              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

	\section{Remainder of the results of the other CR obesity metagenes in \gls{nzbc} data set}
	\label{sec:rest_of_the_cr_ob_meta_heatmap_results_cris}

	All of the other obesity metagenes from the CR data set were able to capture the overall gene expressions of the samples in the \gls{nzbc} data set (\cref{fig:appendix/cr_ob_meta_heatmap_cris}).
	However, none of the CR obesity metagenes were able to significantly associate with the sample \gls{bmi}/\gls{bmi} status in the \gls{nzbc} data set (\cref{fig:appendix/cr_ob_meta_box_scatter_cris}).

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/cris_crdeg_trans_meta}\\
		\includegraphics[width=0.32\linewidth,page=13]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/cris_crdeg_trans_meta}\\
		\includegraphics[width=0.32\linewidth,page=28]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/cris_crdeg_trans_meta}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/cris_crdeg_trans_meta}\\
		\caption{Heatmaps showing the association of the other CR obesity metagenes with the sample gene expression from the \gls{nzbc} data set.
	Scales are as described in previous figures.}
		\label{fig:appendix/cr_ob_meta_heatmap_cris}
	\end{figure}
